\chapter{Implementation}

\subsection{Hypothesis Validation}

To Validate the claims made in the hypothesis, the original technique described by Müller \etal and
the proposed extension will need to be implemented. These implementations will then be used to 
collect data for evaluating the hypothesis.

\subsection{Design}

The original technique and the proposed extensions will be implemented as two applications. The 
first application will be used to generate the voxel-meshes that are needed by both techniques. The
second application will perform the physics simulation. This approach was chosen to remove the need
for voxelization, which can be a costly operation when implemented in a naive fashion, to occur at
simulation run time.

\subsection{Libraries and APIs}

Both applications will make use of a number of libraries and APIs to achieve their respective goals. 
The following is a comprehensive list of the libraries that will be used:

% TODO: links
\begin{itemize}
  \item Bullet Physics: An open source physics engine.
  \item OpenGL: The Open Graphics Library.
  \item GLM: A math library compatible with GLSL math functions.
  \item GLAD: An OpenGL extension loader.
  \item nlohmann/json.hpp: An open source json library for C++.
  \item Dear ImGui: A simple to use, immediate-mode GUI library.
\end{itemize}
%% Obviously you need to delete these lines when you have written up your text

% (Note: this chapter may be merged with Chapter 2 to have a combined Design 
% and Implementation chapter, if more appropriate.)

% \begin{itemize}
% \item{} Software details (use as many section as needed for class design, 
% database tables, middleware, etc.)

% \item{} Make sure you present and comment on any interesting issues about
% your implementation that you are proud of or unhappy with

% \item{} Skip code listing and specific UML diagrams, etc. to an appendix

% \end{itemize}
